OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-11-04 paper/paper.Rmd

Since OptiClust and OptiFit employ a random number generator to break ties
when OTU assignments are of equal quality, they produce slightly different OTU
assignments when repeated with different random seeds.
To capture any variation in OTU quality or execution time, clustering was
repeated with 100 random seeds for each combination of parameters and
input datasets.
We used the benchmark feature provided by Snakemake to measure the run time of
every clustering job.
We calculated the MCC on each set of OTUs to quantify the quality of clustering,
as described by Westcott _et al._ [@westcott_opticlust_2017].

>>>>

OptiClust and OptiFit randomize the order of query sequences prior to clustering
and employ a random number generator to break ties when OTU assignments are of
equal quality.
As a result, they produce slightly different OTU assignments when repeated with
different random seeds.
To capture any variation in OTU quality or execution time, clustering was
repeated with 100 random seeds for each combination of parameters and
input datasets.
We used the benchmark feature provided by Snakemake to measure the run time of
every clustering job.
We calculated the MCC on each set of OTUs to quantify the quality of clustering,
as described by Westcott _et al._ [@westcott_opticlust_2017].
